---
title: "Decision Tree predicting Entrepreneurial Intention"
author: "Ana Karen Reyna Rivas"
date: "2020"
output:
  html_notebook:
    toc: true
    includes:
      after_body: ../Footer.html
bibliography: ../Bibliography.bib
---

```{r}
# Copyright (c) 2020, Ana Karen Reyna Rivas
# All rights reserved.

# This source code is licensed under the BSD-style license found in the LICENSE file in the root directory of this source tree.
```

```{r setup, include=FALSE}
 knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Step 1: Import Libraries
The libraries I used for the whole implementation are imported in this section. The first step was to install the libraries with the `r  colFmt('install.packages()', 'blue')` function. Then, import them with `r  colFmt('library()', 'blue')` function.
```{r}
library(dplyr)
library(knitr)
library(kableExtra) # Construct Complex Table
library(caret)
library(e1071) # R ML Library
library(writexl) # Write to Excel
library(rpart.plot) # Plot rpart
```

# Step 2: Import Data and Functions
The data gathered during the experiment and the reusable code are imported here. The `r  colFmt('load()', 'blue')` function was used to import the data and `r  colFmt('source()', 'blue')` for the code. Additionally, I cleaned the working environment to delete any other existing variables.
```{r}
# Clean Workspace Variables
rm(list = ls())

# Data - TODO
load("<RDataDirectoryFile>")

# Functions
source('../FunctionsV4.R')
source('DT_Functions_wTT.R')
```

# Step 3: Define Global Variables
This section defines all the global variables used across the R Notebook. Variables like size of the train/test split, seed, train control, and features selected for the model are declared here. In case new settings and variables want to be explored, only this section needs to be changed.
```{r}
# Size and Seed
size = 0.50
seed = 6

# Data Frame to Save Table's Values
dataframePreliminarValues <- data.frame()
dataframeTestValues <- data.frame()

# Control K-Fold CV
trControl <- trainControl(method = "cv", number = 10, search = "grid")

######### VARIABLES FOR ALL VERSIONS #########
# Class
class <- c('SplitEntrepreneurIntention')
# Variables
variables <- c('SumNarcissisticPI', 'SumEthicsPositionsRelativismQs', 'MeanOpenness', 'Typerulebreaking')
# All Variables
all_variables <- c(variables, class)

######### VARIABLES FOR VERSION 1 #########
# Class
class_v1 <- c('SplitEntrepreneurIntention')
# Variables
variables_v1 <- c('Narcissism', 'Relativism', 'Openness', 'Typerulebreaking')
# All Variables
all_variables_v1 <- c(variables_v1, class_v1)
```

# Step 4: Filter Data
The data has three types of rule breakers: the Unconditional Rule Followers (URF), the Conditional Rule Breakers (CRB) and the Unconditional Rule Breakers (URB). For this research, only the URF and CRB will be studied.

In the following lines of code, I selected the observations with a `r  colFmt('Typerulebreaking', 'blue')` different than "3", that means different than "URB" type.

Typerulebreaking Factors are:

* 1: URF
* 2: CRB
* 3: URB

I also mutated to the dataframe the `r  colFmt('SplitEntrepreneurIntention', 'blue')` variable as follows:

* If the `r  colFmt('MeanEntrepreneurIntention', 'blue')` value of the instance is lower than the mean of the whole dataset, then "SplitEntrepreneurIntention = 1" (meaning low \gls{ei}).
* If the `r  colFmt('MeanEntrepreneurIntention', 'blue')` value of the instance is higher or equal than the mean of the whole dataset, then "SplitEntrepreneurIntention = 2" (meaning high \gls{ei}).
* Else "SplitEntrepreneurIntention = 3".
```{r}
# Filter and Mutate EI Variable
df_QueParadigmRuleEntIntention <- df_QueParadigm %>%
  filter(Typerulebreaking != 3) %>%
  filter(exp_part == 3) %>%
  mutate(SplitEntrepreneurIntention = dplyr::if_else((MeanEntrepreneurIntention < mean(df_Que_RuleBreakers$MeanEntrepreneurIntention)), 1, dplyr::if_else((MeanEntrepreneurIntention >= mean(df_Que_RuleBreakers$MeanEntrepreneurIntention)), 2, 3)))
# 1 = low EI
# 2 = high EI

# Print First Rows of Data Frame
head(df_QueParadigmRuleEntIntention)
```

# Step 5: Shuffle, Clean and Create Data Samples
It is important to shuffle the data, because then the algorithm will learn from the features of all observations [@Guru99DT] and not only for certain type of rule breaking.

Data clean up to be done as follows [@Guru99DT]:

* Drop variables.
* Create factor variables for "Typerulebreaking".
* Drop NA: in case there are some observations with NA's variables.

The data samples are done using stratified sampling. Its goal is to have control over the number of "Typerulebreaking" sampled from each type [@DataCampStratifiedSample].

By using stratified sample, I will now have control over how many "Typerulebreaking" from each type (URF, CRB) got sampled. I use prop.table() combined with table() to verify if the randomization process is correct [@Guru99DT].
```{r}
# Shuffle Data
df_final <- shuffle_data(df_QueParadigmRuleEntIntention, seed)

# Clean Data
clean_df_final <- data.frame(clean_data(df_final, all_variables))

######### URF DATA #########
df_URF <- clean_df_final %>%
  dplyr::filter(Typerulebreaking == 'URF')
dim(df_URF)

# Stratified Sample URF
data_stratified_sample_URF <- stratified_sample_TT(df_URF, class, size, seed)
data_train_URF <- data_stratified_sample_URF$data_train
data_test_URF <- data_stratified_sample_URF$data_test

dim(data_train_URF)
dim(data_test_URF)

# SplitEntrepreneurIntention is equally divided in each set
prop.table(table(data_train_URF$SplitEntrepreneurIntention))
prop.table(table(data_test_URF$SplitEntrepreneurIntention))

######### CRB DATA #########
df_CRB <- clean_df_final %>%
  dplyr::filter(Typerulebreaking == 'CRB')
dim(df_CRB)

# Stratified Sample CRB
data_stratified_sample_CRB <- stratified_sample_TT(df_CRB, class, size, seed)
data_train_CRB <- data_stratified_sample_CRB$data_train
data_test_CRB <- data_stratified_sample_CRB$data_test

dim(data_train_CRB)
dim(data_test_CRB)

# SplitEntrepreneurIntention is equally divided in each set
prop.table(table(data_train_CRB$SplitEntrepreneurIntention))
prop.table(table(data_test_CRB$SplitEntrepreneurIntention))
```

# Version 1
Formula = SplitEntrepreneurIntention = Narcissism + Relativism + Openness + Typerulebreaking

## URF
### Step 6: Select Sample Variables
```{r}
# Data Train URF
data_train_v1_URF <- data_train_URF %>%
  dplyr::select(c(all_variables_v1))

# Data Test URF
data_test_v1_URF <- data_test_URF %>%
  dplyr::select(c(all_variables_v1))

dim(data_train_v1_URF)
dim(data_test_v1_URF)
```

Use function prop.table() combined with table() to verify if the randomization process is correct.
```{r}
prop.table(table(data_train_v1_URF$SplitEntrepreneurIntention))
prop.table(table(data_test_v1_URF$SplitEntrepreneurIntention))
```
In both dataset, the amount of low and high EI is the same.

### Step 7: Model 1: Default Setting
Create a classification decision tree using "Typerulebreaking" as the variable we want to predict and everything else as its predictors [@IBMCognitiveClass2017].
```{r}
# Get Model 1
model1_v1_URF <- get_model1_dt_TT('1.1 - URF', seed, data_train_v1_URF, trControl)
fit_m1_v1_URF <- model1_v1_URF$fit

# Final Model
fit_m1_v1_URF$finalModel

# Evaluation Model Measures
accuracy_model1_v1_URF <- model1_v1_URF$accuracyTest
kappa_model1_v1_URF <- model1_v1_URF$kappaTest
cp_model1_v1_URF <- model1_v1_URF$bestCP
```
The final value used for the model was cp = `r  cp_model1_v1_URF` with an accuracy = `r  accuracy_model1_v1_URF`% and a kappa = `r  kappa_model1_v1_URF`.

Get the importance of the variables.
```{r}
# Variable Importance
print(varImp(fit_m1_v1_URF), surrogates = FALSE, competes = TRUE)
```

### Step 8: Model 2: Getting Best Control Parameters
DT has parameters that control aspects of the fit [@Guru99DT] and by using the rpart.control() function I can control this parameters by selecting the best values with the target of obtaining the desired performance.
```{r}
# Get Model 2
model2_v1_URF <- get_model2_dt_TT('1.2 - URF', seed, fit_m1_v1_URF, data_train_v1_URF, trControl)
fit_m2_v1_URF <- model2_v1_URF$fit

# Final Model
fit_m2_v1_URF$finalModel

# Evaluation Model Measures Test Data
accuracy_model2_v1_URF <- model2_v1_URF$accuracyTest
kappa_model2_v1_URF <- model2_v1_URF$kappaTest
cp_model2_v1_URF <- model2_v1_URF$bestCP
```
The final value used for the model was cp = `r  cp_model2_v1_URF` with an accuracy = `r  accuracy_model2_v1_URF`% and a kappa = `r  kappa_model2_v1_URF`%.

Get the importance of the variables.
```{r}
# Variable Importance
print(varImp(fit_m2_v1_URF), surrogates = FALSE, competes = TRUE)
```

### Step 9: Evaluate Best Model with Test Data
Make predictions with the best URF model by using the predict() function.
```{r include = FALSE}
# Get Number of Best Model
best_model_v1_URF <- 0
if(accuracy_model1_v1_URF < accuracy_model2_v1_URF) {
  best_model_v1_URF = 2
} else {
  best_model_v1_URF = 1
}

best_fit_v1_URF <- paste('fit_m', best_model_v1_URF, '_v1_URF', sep = "")
```
The model 1 has an accuracy = `r  accuracy_model1_v1_URF`%.
The model 2 has an accuracy = `r  accuracy_model2_v1_URF`%.
As model `r  best_model_v1_URF` demonstrates a better performance, I will use it to evaluate the best model for this version.

```{r}
# Evaluate Model with Test Data
evaluateModelMeasuresTest <- evaluateModel(get(best_fit_v1_URF), data_test_v1_URF, seed)
accuracyTest_v1_URF <- evaluateModelMeasuresTest$accuracy
kappaTest_v1_URF <- evaluateModelMeasuresTest$kappa
sensitivityTest_v1_URF <- evaluateModelMeasuresTest$sensitivity
specificityTest_v1_URF <- evaluateModelMeasuresTest$specificity
```

## CRB
### Step 6: Select Sample Variables
```{r}
# Data Train CRB
data_train_v1_CRB <- data_train_CRB %>%
  dplyr::select(c(all_variables_v1))

# Data Test CRB
data_test_v1_CRB <- data_test_CRB %>%
  dplyr::select(c(all_variables_v1))

dim(data_train_v1_CRB)
dim(data_test_v1_CRB)
```

Use function prop.table() combined with table() to verify if the randomization process is correct.
```{r}
prop.table(table(data_train_v1_CRB$SplitEntrepreneurIntention))
prop.table(table(data_test_v1_CRB$SplitEntrepreneurIntention))
```
In both dataset, the amount of low and high EI is the same.

### Step 7: Model 1: Default Setting
Create a classification decision tree using "Typerulebreaking" as the variable we want to predict and everything else as its predictors [@IBMCognitiveClass2017].
```{r}
# Get Model 1
model1_v1_CRB <- get_model1_dt_TT('1.1 - CRB', seed, data_train_v1_CRB, trControl)
fit_m1_v1_CRB <- model1_v1_CRB$fit

# Final Model
fit_m1_v1_CRB$finalModel

# Evaluation Model Measures
accuracy_model1_v1_CRB <- model1_v1_CRB$accuracyTest
kappa_model1_v1_CRB <- model1_v1_CRB$kappaTest
cp_model1_v1_CRB <- model1_v1_CRB$bestCP
```
The final value used for the model was cp = `r  cp_model1_v1_CRB` with an accuracy = `r  accuracy_model1_v1_CRB`% and a kappa = `r  kappa_model1_v1_CRB`.

Get the importance of the variables.
```{r}
# Variable Importance
print(varImp(fit_m1_v1_CRB), surrogates = FALSE, competes = TRUE)
fit_m1_v1_CRB
```

### Step 8: Model 2: Getting Best Control Parameters
DT has parameters that control aspects of the fit [@Guru99DT] and by using the rpart.control() function I can control this parameters by selecting the best values with the target of obtaining the desired performance.
```{r}
# Get Model 2
model2_v1_CRB <- get_model2_dt_TT('1.2 - CRB', seed, fit_m1_v1_CRB, data_train_v1_CRB, trControl)
fit_m2_v1_CRB <- model2_v1_CRB$fit

# Final Model
fit_m2_v1_CRB$finalModel

# Evaluation Model Measures Test Data
accuracy_model2_v1_CRB <- model2_v1_CRB$accuracyTest
kappa_model2_v1_CRB <- model2_v1_CRB$kappaTest
cp_model2_v1_CRB <- model2_v1_CRB$bestCP
```
The final value used for the model was cp = `r  cp_model2_v1_CRB` with an accuracy = `r  accuracy_model2_v1_CRB`% and a kappa = `r  kappa_model2_v1_CRB`%.

Get the importance of the variables.
```{r}
# Variable Importance
print(varImp(fit_m2_v1_CRB), surrogates = FALSE, competes = TRUE)
```

### Step 9: Evaluate Model with Test Data
Make predictions with the best CRB model by using the predict() function.
```{r include = FALSE}
# Get Number of Best Model
best_model_v1_CRB <- 0
if(accuracy_model1_v1_CRB < accuracy_model2_v1_CRB) {
  best_model_v1_CRB = 2
} else {
  best_model_v1_CRB = 1
}

best_fit_v1_CRB <- paste('fit_m', best_model_v1_CRB, '_v1_CRB', sep = "")
```
The model 1 has an accuracy = `r  accuracy_model1_v1_CRB`%.
The model 2 has an accuracy = `r  accuracy_model2_v1_CRB`%.
As model `r  best_model_v1_CRB` demonstrates a better performance, I will use it to evaluate the best model for this version.

```{r}
# Evaluate Model with Test Data
evaluateModelMeasuresTest <- evaluateModel(get(best_fit_v1_CRB), data_test_v1_CRB, seed)
accuracyTest_v1_CRB <- evaluateModelMeasuresTest$accuracy
kappaTest_v1_CRB <- evaluateModelMeasuresTest$kappa
sensitivityTest_v1_CRB <- evaluateModelMeasuresTest$sensitivity
specificityTest_v1_CRB <- evaluateModelMeasuresTest$specificity
```

# Step 10: Summary
```{r include = FALSE}
# Get Summary
formula_v1 <- 'Entrepreneur Intention = Narcissism + Relativism + Openness'

######## Preliminar Evaluation Model - Train Set ########
# URF
dataframePreliminarValues <- saveFinalSummaryTable_dt_TT_2(dataframePreliminarValues, 1, 
                                            'URF',
                                            accuracy_model1_v1_URF,
                                            kappa_model1_v1_URF,
                                            accuracy_model2_v1_URF,
                                            kappa_model2_v1_URF)

# CRB
dataframePreliminarValues <- saveFinalSummaryTable_dt_TT_2(dataframePreliminarValues, 2, 
                                            'CRB',
                                            accuracy_model1_v1_CRB,
                                            kappa_model1_v1_CRB,
                                            accuracy_model2_v1_CRB,
                                            kappa_model2_v1_CRB)

######## Final Evaluation Model - Test Set ########
# URF
dataframeTestValues <- saveFinalSummaryTable_dt_TT(dataframeTestValues, 1, 
                                                    'URF',
                                                    best_model_v1_URF,
                                                    accuracyTest_v1_URF,
                                                    kappaTest_v1_URF,
                                                    sensitivityTest_v1_URF,
                                                    specificityTest_v1_URF,
                                                    as.matrix(varImp(get(best_fit_v1_URF), surrogates = TRUE)$importance))

# CRB
dataframeTestValues <- saveFinalSummaryTable_dt_TT(dataframeTestValues, 2, 
                                                    'CRB',
                                                    best_model_v1_CRB,
                                                    accuracyTest_v1_CRB,
                                                    kappaTest_v1_CRB,
                                                    sensitivityTest_v1_CRB,
                                                    specificityTest_v1_CRB,
                                                    as.matrix(varImp(get(best_fit_v1_CRB), surrogates = TRUE)$importance))
```

## Preliminar Performance Summary
```{r echo = FALSE, results = 'asis'}
# Change Name of Columns
colnames(dataframePreliminarValues) <- c("TRB", "Accuracy", 'Kappa', 'Accuracy', 'Kappa')

# Print Data Frame
kable(dataframePreliminarValues, "html", caption = "Preliminar Performance Summary")%>%
  kable_styling(bootstrap_options = c("condensed", "responsive")) %>%
  collapse_rows(1)%>%
  add_header_above(c(" ", "Model 1" = 2, "Model 2" = 2))
```

## Final Performance Summary
```{r echo = FALSE, results = 'asis'}
# Change Name of Columns
colnames(dataframeTestValues) <- c("TRB", "Model", "Accuracy", 'Kappa', 'Sensitivity', 'Specificity', "Variable Importance")

# Print Data Frame
kable(dataframeTestValues, "html", caption = "Final Performance Summary")%>% 
  kable_styling(bootstrap_options = c("condensed", "responsive")) %>%
  collapse_rows(1)

# URF Best Model Plot
split <- paste(size, ":", 1-size, sep = "")

prp(get(best_fit_v1_URF)$finalModel, type = 0, extra = 1, under = TRUE,
    main = paste("DT Split ", split, " - URF Best Model - Model ", best_model_v1_URF, sep = ""))

# CRB Best Model Plot
prp(get(best_fit_v1_CRB)$finalModel, type = 0, extra = 1, under = TRUE,
    main = paste("DT Split ", split, " - CRB Best Model - Model ", best_model_v1_CRB, sep = ""))
```

```{r include = FALSE}
# Save Plots in PDF
## V1
fileName <- paste("DT_V1_BestModelsPlots_Size", size, ".pdf", sep = "" )
pdf(file = fileName)
  # URF Best Model Plot
  prp(get(best_fit_v1_URF)$finalModel, type = 0, extra = 1, under = TRUE,
      main = paste("DT Split ", split, " - URF Best Model - Model ", best_model_v1_URF, sep = ""))
  
  # CRB Best Model Plot
  prp(get(best_fit_v1_CRB)$finalModel, type = 0, extra = 1, under = TRUE,
      main = paste("DT Split ", split, " - CRB Best Model - Model ", best_model_v1_CRB, sep = ""))
dev.off()

# Save Table to Excel
sheets <- list("FinalPerformaceSummary" = dataframeTestValues, "PreliminarPerformaceSummary" = dataframePreliminarValues)
write_xlsx(sheets, paste("performanceSummary_Size", size, ".xlsx", sep = ""))
```